---
title: "Project 2"
author: "Tyler Bryant"
date: "2/20/2026"
output: html_document
---

#Introduction: This dataset is the State-Specific Influenza Vaccination Coverage Among Women with Live Births — PRAMS, 2009–2010 Influenza Season deriving from the Pregnancy Risk Assessment Monitoring System. My objective is to  create a descriptive report analyzing the state level variation in flu vaccine coverage and to examine the disparities in uptake to improve vaccination coverage.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}


library(tidyverse)
library(ggplot2)
library(gtsummary)
library(readr)
flu<- read_csv("https://data.cdc.gov/resource/mmi4-8ajr.csv?$limit=50000") 
```

```{r}
names(flu)
```


```{r}
library(gtsummary)
tbl1<- flu %>%
  select(seasonal) %>%
  tbl_summary(
    statistic=all_continuous()~"{mean} ({sd}) | {median} [{p25}, {p75}]"
  )
print(tbl1)
```

#Table 1 shows the distribution of state level seasonal influenza vaccination coverage among woem with a live birth during the 2009-2010 flu season. The mean vaccination coverage of 49% accross states demonstating variability in vaccination uptake across states.



```{r}
flu %>%
  select(state,seasonal) %>%
  arrange(seasonal) %>%
  mutate(state=fct_inorder(state))%>% 
  ggplot(aes(x=state, y=seasonal)) +
  geom_col()+
  coord_flip()
```
# this figure shows the varied vacination coverage across states. 
